%/*************************************************************************
% *
% * FILE  details.tex
% * $Id: details.tex,v 1.4 2001/09/08 13:59:36 tlr Exp $
% *
% * DESCRIPTION 
% *   The details appendix.
% *
% * This file is part of ztracker - a tracker-style MIDI sequencer.
% *
% * Copyright (c) 2001, Daniel Kahlin <tlr@users.sourceforge.net>
% * All rights reserved.
% *
% * Redistribution and use in source and binary forms, with or without
% * modification, are permitted provided that the following conditions
% * are met:
% * 1. Redistributions of source code must retain the above copyright
% *    notice, this list of conditions and the following disclaimer.
% * 2. Redistributions in binary form must reproduce the above copyright
% *    notice, this list of conditions and the following disclaimer in the
% *    documentation and/or other materials provided with the distribution.
% * 3. Neither the names of the copyright holders nor the names of their
% *    contributors may be used to endorse or promote products derived 
% *    from this software without specific prior written permission.
% *
% * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
% * ``AS IS´´ AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
% * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
% * A PARTICULAR PURPOSE ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR
% * CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
% * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO,
% * PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
% * PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
% * LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
% * NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
% * SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
% *
% ******/
\chapter{Details}

% processing order

\section{Processing Order}
  Tracks are processed in ascending order.  Any commands/data in track 1
is processed and sent before commands/data in track 2, and so on\ldots{}
Each track has its own parameter memory.  For example, if you play the same
midi channel from both track 1 and 2 and do a pitch slide in track 1, when you
try continue the pitch slide from track 2, it will start from the same point
that track 1 started from.


% pitch bend values

\section{Pitch Bend Values}
  Pitch effects are ways of setting the MIDI Pitch bend value.  Normally a synth has
a pitch bend \emph{range} defined for each sound.  This \emph{range} determines how
many semitones the pitch is shifted for the maximum pitch bend \emph{value}, up or down.
Mosts synths allow you to set the range to between 0 and 12, some even up to 24
(two octaves)

% pitch bend formulae
The pitch bend value corresponding to a particular number of semitones pitch shift can
be calculated by the following formula:

\begin{equation}
value=round\biggl( 8192 + \frac{8192}{range} \cdot \Delta P_{semi} \biggr)
\end{equation}

Or if cents are preferred:

\begin{equation}
value=round\biggl( 8192 + \frac{8192}{range \cdot 100} \cdot \Delta P_{cents} \biggr)
\end{equation}

Note that these formulae gives values from 0 to 16384, and that pitch bend values
range from 0 to 16383.  To solve this 16384 is replaced with 16383, the error
introduced is unnoticable. 

% Pitch slides
\section{Pitch Slides}
  Pitch slides are instructions to the player to update the pitch bend value every
subtick (which is 24 ppqn). $ticks$ is the duration of the slide in number of rows.
$tpb$ is the number of ticks per beat. $\Delta_{value}$ is the desired resulting pitch bend
change after $ticks$ ticks have elapsed.  $slide$ is the parameter to use with the
slide command.
\begin{equation}
slide=round\biggl( \Delta_{value} \cdot \frac{tpb}{subticks \cdot ticks} \biggr)
\end{equation}
This equation can then be merged with the previous pitch formulae.
\begin{equation}
slide=round\Biggl( \biggl( \frac{8192}{range} \cdot \Delta P_{semi} \biggr) \cdot \frac{tpb}{24 \cdot ticks} \Biggr)
\end{equation}
\begin{equation}
slide=round\Biggl( \biggl( \frac{8192}{range \cdot 100} \cdot \Delta P_{cents} \biggr) \cdot \frac{tpb}{24 \cdot ticks} \Biggr)
\end{equation}


% pitchbend tables
\input{pitchtables}

% eof
